The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-06-30 src/tex/ms.tex
[showyourwork] overleaf sync

% Author list
\author[0000-0003-3781-0747]{Liam O. Dubay}
\author[0000-0001-7258-1834]{Jennifer A. Johnson}
\author[0000-0002-6534-8783]{James W. Johnson}
\author[0000-0001-7775-7261]{David H. Weinberg}

@@

\paragraph{Two-infall} 
We parameterize the infall rate as two successive, exponentially declining bursts as in \citet{Chiappini2001-AbundanceGradients}:
\begin{equation}
    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2}
\end{equation}
with normalization coefficients
\begin{equation}
    N_1(R_{\rm gal}) = \frac{\Sigma_{1,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_1}}{\tau_1 (1-e^{-t_{\rm max}/\tau_1})}
\end{equation}
and
\begin{equation}
    N_2(R_{\rm gal}) = \frac{\Sigma_{2,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_2}}{\tau_2 (1-e^{-(t_{\rm max}-t_{\rm on})/\tau_2})}
\end{equation}
Second infall onset time $t_{\rm on}=4$ Gyr, infall timescales $\tau_1=1$ Gyr and $\tau_2=4$ Gyr. We take the surface mass density ratio of the thin disk to the thick disk at the Sun to be $(\frac{\Sigma_2}{\Sigma_1})_\odot=5.6$ \citep{Spitoni2021-TwoInfall}.

>>>>

% Author list
\author[0000-0003-3781-0747]{Liam O. Dubay}
\author[0000-0001-7258-1834]{Jennifer A. Johnson}
\author[0000-0002-6534-8783]{James W. Johnson}
% \author[0000-0001-7775-7261]{David H. Weinberg}

@@

\paragraph{Two-infall} 
We parameterize the infall rate as two successive, exponentially declining bursts as in \citet{Chiappini2001-AbundanceGradients}:
\begin{equation}
    \label{eq:twoinfall-ifr}
    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2}
\end{equation}
% with normalization coefficients
% \begin{equation}
%     N_1(R_{\rm gal}) = \frac{\Sigma_{1,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_1}}{\tau_1 (1-e^{-t_{\rm max}/\tau_1})}
% \end{equation}
% and
% \begin{equation}
%     N_2(R_{\rm gal}) = \frac{\Sigma_{2,\odot} e^{-(R_{\rm gal}-8\,\rm{kpc})/R_2}}{\tau_2 (1-e^{-(t_{\rm max}-t_{\rm on})/\tau_2})}
% \end{equation}
% Second infall onset time $t_{\rm on}=4$ Gyr, infall timescales $\tau_1=1$ Gyr and $\tau_2=4$ Gyr. We take the surface mass density ratio of the thin disk to the thick disk at the Sun to be $(\frac{\Sigma_2}{\Sigma_1})_\odot=5.6$ \citep{Spitoni2021-TwoInfall}.
The normalization ratio $N_2/N_1$ is calculated so that the ratio of stellar surface mass density produced by the second infall relative to the first follows
\begin{equation}
    \frac{\Sigma_2}{\Sigma_1} = \Big(\frac{\Sigma_2}{\Sigma_1}\Big)_{R_0} e^{(R-R_0)(1/h{R,2} - 1/h_{R,1})}
\end{equation}
where $h_{R,1}=2.0$ kpc and $h_{R,2}=3.5$ kpc are the thick- and thin-disk scale radii, respectively, found by \citet{Bovy2012-SubPopulationStructure}. We take the local thick- to thin-disk surface density ratio $(\Sigma_1/\Sigma_2)_{R_0}=0.05$ for [reasons].
